---
title: "Hearing impairment study - Results"
output:
  word_document:
    reference_docx: template.docx
  pdf_document: default

---

Date: `r Sys.Date()`

```{r include=FALSE}
# load libraries
lib <- c("magrittr", "tidyverse", "ggplot2",
         "knitr", "grid", "gridExtra")
lapply(lib, require, character.only = TRUE)
rm(lib)

# load ws
load("ws_27_05_18.RData")

# set plot folder
knitr::opts_chunk$set(
  fig.path = "images/"
)
```

<!-- additional funs -->
```{r echo = FALSE}
grid_arrange_shared_legend <- function(..., nrow = 1,y_title, x_size, y_size,widths1 = 2, widths2=0.2,hjust1=1, x_title, ncol = length(list(...)), position = c("bottom", "right")) {

  plots <- list(...)
  position <- match.arg(position)
  g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  lwidth <- sum(legend$width)
  gl <- lapply(plots, function(x) x + theme(legend.position = "none"))
  gl <- c(gl, nrow = nrow, ncol = ncol)

  combined <- switch(position,
                     "bottom" = arrangeGrob(do.call(arrangeGrob, gl),
                                            legend,
                                            ncol = 1,
                                            heights = unit.c(unit(1, "npc") - lheight, lheight)),
                     "right" = arrangeGrob(do.call(arrangeGrob, gl),
                                           legend,
                                           ncol = 2,
                                           widths = c(widths1, widths2),
                                           left=textGrob(y_title, gp=gpar(fontsize=y_size), rot = 90),
                                           bottom=textGrob(x_title, gp=gpar(fontsize=x_size), vjust = 0, hjust = hjust1)))
  grid.newpage()
  grid.draw(combined)

}
```

<br>

## Summary vocabulary

<br>

#### Table

Number of correct and incorrect words. Proportion of incorrect words learned by each model (phonetic transcription considered), based on "total number of words produced by the model" or "total number of words produced by the mother" (*N* = `r n_phon_mot`).

```{r echo=FALSE}
mods_summary %>%
  rename(Models = mod, `Correct tokens` = phon_corr_tokens,
         `Incorrect tokens`= phon_inc_tokens, 
         `Proportion incorrect tokens` = prop_phon_inc,
         `Proportion incorrect tokens (Mot)` = `prop_phon_inc (mot)`) %>%
  kable()
```

<br>

#### Table

Cumulative proportion of incorrect words learned by each model by stage, based on "total number of words produced by the mother" (*N* = `r n_phon_mot`).

```{r echo=FALSE}
mods_summary_stage %>%
  rename(Models = models) %>%
  kable()
```

<br>

## Phonotactic Probability (PP) and Phonological Neighbourhood Density (PN) (original words for incorrect vocabulary)

<br>

#### Table

PP quartiles

```{r echo=FALSE}
qu_pp %>%
  t() %>%
  as_tibble() %>%
  kable()
```

<br>

```{r echo=FALSE}
qu_pn %>%
  t() %>%
  as_tibble() %>%
  kable()
```

<br>

```{r echo=FALSE, fig.width=16, fig.height=9, message=FALSE, warning=FALSE}
# create a function to plot pn or pp for a single df
p_plot <- function(df, title, p_type) {
  if (p_type == "pp") {
    ggplot(df, aes(x=section, y=pp_qu1perc, fill=baby, shape="Q1")) + 
      geom_point(size=4, alpha=0.2) +
      scale_x_continuous(breaks=c(1, seq(5,20, 5))) +
      labs(x = " ", y = " ") +
      ggtitle(title) +
      theme(plot.title = element_text(hjust = 0.5, size = 12.5)) +
      geom_point(aes(x=section, y=pp_qu2perc, fill=baby, shape="Q2"),size=4, alpha=0.2) + 
      geom_point(aes(x=section, y=pp_qu3perc, fill=baby, shape="Q3"), size=4,alpha=0.2) + 
      geom_point(aes(x=section, y=pp_qu4perc, fill=baby, shape="Q4"), size=4,alpha=0.2) + 
      scale_shape_manual("IPhOD Quartile", values=c(`Q1`= 0, `Q2`= 3, `Q3` = 2, `Q4`=1),
                         breaks=c("Q1","Q2", "Q3","Q4"))+
      scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 20))+
      guides(fill=FALSE)+
      geom_smooth(aes(x=section, y=pp_qu1perc,linetype="Q1"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      geom_smooth(aes(x=section, y=pp_qu2perc,linetype="Q2"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      geom_smooth(aes(x=section, y=pp_qu3perc,linetype="Q3"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      geom_smooth(aes(x=section, y=pp_qu4perc,linetype="Q4"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      theme(axis.text=element_text(size=18), legend.text = element_text(size = 20), 
            legend.title = element_text(size = 20), legend.key.size = unit(1, "cm")) +
      scale_colour_grey(start = 0, end = .9)+
      scale_linetype_manual("IPhOD Quartile", values=c(`Q4` = "dotdash", `Q1` = "longdash",
                                                       `Q2` = "solid", `Q3`= "dotted"), 
                            breaks=c("Q1","Q2", "Q3","Q4"))
  } else if (p_type == "pn") {
    ggplot(df, aes(x=section, y=pn_qu1perc, fill=baby, shape="Q1")) + 
      geom_point(size=4, alpha=0.2) +
      scale_x_continuous(breaks=c(1, seq(5,20, 5))) +
      labs(x = " ", y = " ") +
      ggtitle(title) +
      theme(plot.title = element_text(hjust = 0.5, size = 12.5)) +
      geom_point(aes(x=section, y=pn_qu2perc, fill=baby, shape="Q2"), size=4,alpha=0.2) + 
      geom_point(aes(x=section, y=pn_qu3perc, fill=baby, shape="Q3"), size=4,alpha=0.2) + 
      geom_point(aes(x=section, y=pn_qu4perc, fill=baby, shape="Q4"), size=4,alpha=0.2) + 
      scale_shape_manual("IPhOD Quartile", values=c(`Q1`= 0, `Q2`= 3, `Q3` = 2, `Q4`=1),
                         breaks=c("Q4", "Q3","Q2","Q1"))+
      scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 20))+
      guides(fill=FALSE)+
      geom_smooth(aes(x=section, y=pn_qu1perc,linetype="Q1"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      geom_smooth(aes(x=section, y=pn_qu2perc,linetype="Q2"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      geom_smooth(aes(x=section, y=pn_qu3perc,linetype="Q3"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      geom_smooth(aes(x=section, y=pn_qu4perc,linetype="Q4"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      theme(axis.text=element_text(size=18),         
            legend.text = element_text(size = 20),         
            legend.title = element_text(size = 20),         
            legend.key.size = unit(1, "cm"))+     
      scale_colour_grey(start = 0, end = .9)+
      scale_linetype_manual("IPhOD Quartile", values=c(`Q4` = "dotdash", `Q1` = "longdash",
                                                       `Q2` = "solid", `Q3`= "dotted"), 
                            breaks=c("Q4","Q3","Q2","Q1"))
  }
}

# create a list of plots
p_list <- lapply(filenames, function(x) {
  plot_pp <- p_plot(mods_iph[[x]], paste("PP", x, ""), "pp")
  plot_pn <- p_plot(mods_iph[[x]], paste("PN", x, ""), "pn")
  list(plot_pp = plot_pp, plot_pn = plot_pn)
}) %>%
  (function(x) {
    names(x) <- filenames
    x
  })

# function to plot 4 graphs at a time
names_cat0 <- filenames[grepl("error-0$",filenames)]
names_cat <- filenames %>%
  (function(x) {
    gsub("-error-[0-9]{2}{1}[.][0-9]{1}|-error-0$", "", x) %>%
      unique()
  })

# print all plots
p_plot4 <- function(names_cat) {
  grid_arrange_shared_legend(p_list[[names_cat[1]]][[1]],p_list[[names_cat[2]]][[1]],
                             p_list[[names_cat[3]]][[1]],p_list[[names_cat[4]]][[1]],
                             position = "right", x_title = "Stage", y_title = "Novel words (%)",
                             x_size = 25, y_size = 25, widths1 = 2, widths2 = 0.5, hjust1 = 1)
}
  
p_plot4(names_cat0)
```

<br>

```{r echo=FALSE, fig.width=16, fig.height=9, message=FALSE, warning=FALSE}
for (i in names_cat) {
  names_cat <- filenames[grepl(i, filenames)] %>%
    (function(x) {x[!x %in% names_cat0]})
  
  p_plot4(names_cat)
}
```

