---
title: "Hearing impairment study - Results"
output:
  word_document:
    reference_docx: template.docx
  pdf_document: default

---

Date: `r Sys.Date()`

```{r include=FALSE}
# load libraries
lib <- c("magrittr", "tidyverse", "ggplot2",
         "knitr", "grid", "gridExtra")
lapply(lib, require, character.only = TRUE)
rm(lib)

# load ws
load("ws_27_05_18.RData")

# set plot folder
knitr::opts_chunk$set(
  fig.path = "images/"
)
```

<!-- additional funs -->
```{r echo = FALSE}
grid_arrange_shared_legend <- function(..., nrow = 1, y_title, x_size, y_size, 
                                       widths1 = 2, widths2=0.2, 
                                       hjust1=1, x_title, 
                                       ncol = length(list(...)), 
                                       position = c("bottom", "right")) {

  plots <- list(...)
  position <- match.arg(position)
  g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  lwidth <- sum(legend$width)
  gl <- lapply(plots, function(x) x + theme(legend.position = "none"))
  gl <- c(gl, nrow = nrow, ncol = ncol)

  combined <- switch(position,
                     "bottom" = arrangeGrob(do.call(arrangeGrob, gl),
                                            legend,
                                            ncol = 1,
                                            heights = unit.c(unit(1, "npc") - lheight, lheight)),
                     "right" = arrangeGrob(do.call(arrangeGrob, gl),
                                           legend,
                                           ncol = 2,
                                           widths = c(widths1, widths2),
                                           left=textGrob(y_title, gp=gpar(fontsize=y_size), rot = 90),
                                           bottom=textGrob(x_title, gp=gpar(fontsize=x_size), vjust = 0, hjust = hjust1)))
  grid.newpage()
  grid.draw(combined)

}
```

<br>

## Index

- Summary vocabulary;
- Phonotactic Probability (PP) and Phonological Neighbourhood Density (PN). Original words for incorrect vocabulary;
- cumulative frequency of incorrect vocabulary and original vocabulary for incorrect words;
- incorrect replacement.

<br>

## Summary vocabulary

<br>

#### Table

Number of correct and incorrect words. Proportion of incorrect words learned by each model (phonetic transcription considered), based on "total number of words produced by the model" or "total number of words produced by the mother" (*N* = `r n_phon_mot`).

```{r echo=FALSE}
mods_summary %>%
  rename(Models = mod, `Correct tokens` = phon_corr_tokens,
         `Incorrect tokens`= phon_inc_tokens, 
         `Proportion incorrect tokens` = prop_phon_inc,
         `Proportion incorrect tokens (Mot)` = `prop_phon_inc (mot)`) %>%
  kable()
```

<br>

#### Table

Cumulative proportion of incorrect words learned by each model by stage, based on "total number of words produced by the mother" (*N* = `r n_phon_mot`).

```{r echo=FALSE}
mods_summary_stage %>%
  rename(Models = models) %>%
  kable()
```

<br>

## Phonotactic Probability (PP) and Phonological Neighbourhood Density (PN) (original words for incorrect vocabulary)

<br>

#### Table

PP quartiles

```{r echo=FALSE}
qu_pp %>%
  t() %>%
  as_tibble() %>%
  kable()
```

<br>

#### Table

PN quartiles

```{r echo=FALSE}
qu_pn %>%
  t() %>%
  as_tibble() %>%
  kable()
```

<br>

```{r echo=FALSE, fig.width=16, fig.height=9, message=FALSE, warning=FALSE}
# create a function to plot pn or pp for a single df
p_plot <- function(df, title, p_type) {
  if (p_type == "pp") {
    ggplot(df, aes(x=section, y=pp_qu1perc, fill=baby, shape="Q1")) + 
      geom_point(size=4, alpha=0.2) +
      scale_x_continuous(breaks=c(1, seq(5,20, 5))) +
      labs(x = " ", y = " ") +
      ggtitle(title) +
      theme(plot.title = element_text(hjust = 0.5, size = 12.5)) +
      geom_point(aes(x=section, y=pp_qu2perc, fill=baby, shape="Q2"),size=4, alpha=0.2) + 
      geom_point(aes(x=section, y=pp_qu3perc, fill=baby, shape="Q3"), size=4,alpha=0.2) + 
      geom_point(aes(x=section, y=pp_qu4perc, fill=baby, shape="Q4"), size=4,alpha=0.2) + 
      scale_shape_manual("IPhOD Quartile", values=c(`Q1`= 0, `Q2`= 3, `Q3` = 2, `Q4`=1),
                         breaks=c("Q1","Q2", "Q3","Q4"))+
      scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 20))+
      guides(fill=FALSE)+
      geom_smooth(aes(x=section, y=pp_qu1perc,linetype="Q1"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      geom_smooth(aes(x=section, y=pp_qu2perc,linetype="Q2"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      geom_smooth(aes(x=section, y=pp_qu3perc,linetype="Q3"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      geom_smooth(aes(x=section, y=pp_qu4perc,linetype="Q4"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      theme(axis.text=element_text(size=18), legend.text = element_text(size = 20), 
            legend.title = element_text(size = 20), legend.key.size = unit(1, "cm")) +
      scale_colour_grey(start = 0, end = .9)+
      scale_linetype_manual("IPhOD Quartile", values=c(`Q4` = "dotdash", `Q1` = "longdash",
                                                       `Q2` = "solid", `Q3`= "dotted"), 
                            breaks=c("Q1","Q2", "Q3","Q4"))
  } else if (p_type == "pn") {
    ggplot(df, aes(x=section, y=pn_qu1perc, fill=baby, shape="Q1")) + 
      geom_point(size=4, alpha=0.2) +
      scale_x_continuous(breaks=c(1, seq(5,20, 5))) +
      labs(x = " ", y = " ") +
      ggtitle(title) +
      theme(plot.title = element_text(hjust = 0.5, size = 12.5)) +
      geom_point(aes(x=section, y=pn_qu2perc, fill=baby, shape="Q2"), size=4,alpha=0.2) + 
      geom_point(aes(x=section, y=pn_qu3perc, fill=baby, shape="Q3"), size=4,alpha=0.2) + 
      geom_point(aes(x=section, y=pn_qu4perc, fill=baby, shape="Q4"), size=4,alpha=0.2) + 
      scale_shape_manual("IPhOD Quartile", values=c(`Q1`= 0, `Q2`= 3, `Q3` = 2, `Q4`=1),
                         breaks=c("Q4", "Q3","Q2","Q1"))+
      scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 20))+
      guides(fill=FALSE)+
      geom_smooth(aes(x=section, y=pn_qu1perc,linetype="Q1"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      geom_smooth(aes(x=section, y=pn_qu2perc,linetype="Q2"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      geom_smooth(aes(x=section, y=pn_qu3perc,linetype="Q3"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      geom_smooth(aes(x=section, y=pn_qu4perc,linetype="Q4"), 
                  fill=NA, colour="black", method="lm", size=0.8)+
      theme(axis.text=element_text(size=18),         
            legend.text = element_text(size = 20),         
            legend.title = element_text(size = 20),         
            legend.key.size = unit(1, "cm"))+     
      scale_colour_grey(start = 0, end = .9)+
      scale_linetype_manual("IPhOD Quartile", values=c(`Q4` = "dotdash", `Q1` = "longdash",
                                                       `Q2` = "solid", `Q3`= "dotted"), 
                            breaks=c("Q4","Q3","Q2","Q1"))
  }
}

# create a list of plots
p_list <- lapply(filenames, function(x) {
  plot_pp <- p_plot(mods_iph[[x]], paste("PP", x, ""), "pp")
  plot_pn <- p_plot(mods_iph[[x]], paste("PN", x, ""), "pn")
  list(plot_pp = plot_pp, plot_pn = plot_pn)
}) %>%
  (function(x) {
    names(x) <- filenames
    x
  })

# function to plot 4 graphs at a time
names_cat0 <- filenames[grepl("error-0$",filenames)]
names_cat <- filenames %>%
  (function(x) {
    gsub("-error-[0-9]{2}{1}[.][0-9]{1}|-error-0$", "", x) %>%
      unique()
  })

# print all plots
p_plot4 <- function(names_cat) {
  grid_arrange_shared_legend(p_list[[names_cat[1]]][[1]],p_list[[names_cat[2]]][[1]],
                             p_list[[names_cat[3]]][[1]],p_list[[names_cat[4]]][[1]],
                             position = "right", x_title = "Stage", y_title = "Novel words (%)",
                             x_size = 25, y_size = 25, widths1 = 2, widths2 = 0.5, hjust1 = 1)
}
  
p_plot4(names_cat0)
```

<br>

```{r echo=FALSE, fig.width=16, fig.height=9, message=FALSE, warning=FALSE}
for (i in names_cat) {
  names_cat <- filenames[grepl(i, filenames)] %>%
    (function(x) {x[!x %in% names_cat0]})
  
  p_plot4(names_cat)
} ; rm(i)
```

<br>

## Cumulative frequency of incorrect vocabulary and original vocabulary for incorrect words

For each participant, cumulative frequency mean was calculated for each stage. The following plots show the average cumulative frequency by stage across participants. The grey bands identify the 95% confidence interval around the mean.

```{r echo=FALSE, fig.width=16, fig.height=9, message=FALSE, warning=FALSE}
# freq plot function
freq_plot <- function(df, title) {
  mod <- df %>%
  mutate(word_type = word_type %>%
           factor(levels = c("inc_or_freq_avg_stage", "inc_freq_avg_stage"),
                  labels = c("Original words", "Incorrect words"))) 

ggplot(mod, aes(x=section, y=freq_avg_stage, shape = word_type)) +
  geom_ribbon(aes(ymin = `CI95%_lower`, ymax = `CI95%_upper`), 
            alpha = 0.5) +
  labs(x = " ", y = " ") +
  ggtitle(title) +
  theme(plot.title = element_text(hjust = 0.5, size = 12.5)) +
  geom_point(size=6) +
  geom_line() +
  scale_fill_manual("Word type",values=c("grey60","grey60")) +
  scale_shape_manual("Word type", values = c(2,8)) +
  theme(legend.title=element_text(size=19), 
        legend.text=element_text(size=19),
        legend.key.size = unit(1, "cm"))
}

# list of frequency plots
p_freq_list <- filenames %>%
  lapply(function(x) {
    freq_plot(mods_freq[[x]], x)
  }) %>%
  (function(x) {
    names(x) <- filenames
    x
  })

names_cat0 <- filenames[grepl("error-0$",filenames)]
names_cat <- filenames %>%
  (function(x) {
    gsub("-error-[0-9]{2}{1}[.][0-9]{1}|-error-0$", "", x) %>%
      unique()
  })

# print all plots
p_freq_plot4 <- function(names_cat) {
  grid_arrange_shared_legend(p_freq_list[[names_cat[1]]],p_freq_list[[names_cat[2]]],
                             p_freq_list[[names_cat[3]]],p_freq_list[[names_cat[4]]],
                             position = "right", x_title = "Stage", 
                             y_title = "Cumulative frequency (mean)",
                             x_size = 25, y_size = 25, widths1 = 2, widths2 = 0.5, hjust1 = 1)
}

p_freq_plot4(names_cat0)
```

```{r echo=FALSE, fig.width=16, fig.height=9, message=FALSE, warning=FALSE}
for (i in names_cat) {
  names_cat <- filenames[grepl(i, filenames)] %>%
    (function(x) {x[!x %in% names_cat0]})
  
  p_freq_plot4(names_cat)
}
```

<br>

## Incorrect word replacement

In the graphs below, the following measures are displayed: 

- the number of incorrect words that have a higher frequency than the original one;
- the number of original words that have a higher frequency than the incorrect one.

<br>

```{r echo=FALSE, fig.width=16, fig.height=9, message=FALSE, warning=FALSE}
# freq plot function
freq_repl_plot <- function(df, title) {
  mod <- df %>%
  mutate(word_type = word_type %>%
           factor(levels = c("inc_or_higher_avg_stage", "inc_higher_avg_stage"),
                  labels = c("original > incorrect", "incorrect > original"))) 

ggplot(mod, aes(x=section, y=higher_avg_stage, shape = word_type)) +
  geom_ribbon(aes(ymin = `CI95%_lower`, ymax = `CI95%_upper`), 
            alpha = 0.5) +
  labs(x = " ", y = " ") +
  ggtitle(title) +
  theme(plot.title = element_text(hjust = 0.5, size = 12.5)) +
  geom_point(size=6) +
  geom_line() +
  scale_fill_manual("Word type",values=c("grey60","grey60")) +
  scale_shape_manual("Word type", values = c(2,8)) +
  theme(legend.title=element_text(size=19), 
        legend.text=element_text(size=19),
        legend.key.size = unit(1, "cm"))
}

# list of frequency plots
p_freq_repl_list <- filenames %>%
  lapply(function(x) {
    freq_repl_plot(mods_freq_repl[[x]], x)
  }) %>%
  (function(x) {
    names(x) <- filenames
    x
  })

names_cat0 <- filenames[grepl("error-0$",filenames)]
names_cat <- filenames %>%
  (function(x) {
    gsub("-error-[0-9]{2}{1}[.][0-9]{1}|-error-0$", "", x) %>%
      unique()
  })

# print all plots
p_freq_repl_plot4 <- function(names_cat) {
  grid_arrange_shared_legend(p_freq_repl_list[[names_cat[1]]],p_freq_repl_list[[names_cat[2]]],
                             p_freq_repl_list[[names_cat[3]]],p_freq_repl_list[[names_cat[4]]],
                             position = "right", x_title = "Stage", 
                             y_title = "Words with a higher frequency (mean)",
                             x_size = 25, y_size = 25, widths1 = 2, widths2 = 0.5, hjust1 = 1)
}

p_freq_repl_plot4(names_cat0)
```

```{r echo=FALSE, fig.width=16, fig.height=9, message=FALSE, warning=FALSE}
for (i in names_cat) {
  names_cat <- filenames[grepl(i, filenames)] %>%
    (function(x) {x[!x %in% names_cat0]})
  
  p_freq_repl_plot4(names_cat)
}
```
